### 2015-04-18 usecase-python.tex
clarify "when this" --> "During the activate operation"

To support this mode of operation, we added the concept of {\tt extension} packages
to Spack. Python modules now use the {\tt extends('python')} directive instead of
{\tt depends\_on('python')}.
Each module installs into its own prefix like any other package,
and each module depends on a particular Python installation.
Additionally, we added the capability to {\tt activate} and {\tt deactivate} an
extension within its dependent Python installation.  When this happens, each file
in the module prefix is symbolically linked into the Python installation prefix, as though it were
directly installed within the Python instance. If any file conflict would arise from this operation,
the activate operation fails and notifies the user.
The deactivate operation removes the symbolic links and restores the Python installation to its 
pristine state.

>>>>

To support this mode of operation, we added the concept of {\tt extension} packages
to Spack. Python modules now use the {\tt extends('python')} directive instead of
{\tt depends\_on('python')}.
Each module installs into its own prefix like any other package,
and each module depends on a particular Python installation.
Additionally, we added the capability to {\tt activate} and {\tt deactivate} an
extension within its dependent Python installation.  During the activate operation, each file
in the module prefix is symbolically linked into the Python installation prefix, as though it were
directly installed within the Python instance. If any file conflict would arise from this operation,
the activate operation fails and notifies the user.
The deactivate operation removes the symbolic links and restores the Python installation to its 
pristine state.
